\textsf{Are frontier models superhuman chemists?}

### 2024-03-18 src/tex/ms.tex
update data description

\subparagraph{Analytical chemistry}
The \variable{output/question_count_per_dir/json_file_counts_analytical_chemistry.txt} questions are based on master student examination papers at the University of Jena (Germany). 
These questions focus on the principles and techniques employed in analytical chemistry.

\subparagraph{Combustion engineering}
These \variable{output/question_count_per_dir/json_file_counts_combustion_engineering.txt} questions are based on master student examination papers at the University of Magdeburg (Germany). 
They explore topics related to combustion processes and engineering principles.

\subparagraph{Functional materials and nanomaterials}
The \variable{output/question_count_per_dir/json_file_counts_func_mats_and_nanomats.txt}  questions are based on exercises in a seminar conducted at the University of Jena (Germany), delving into topics concerning functional materials and nanomaterials, exploring their properties and applications.

@@

>>>>

\subparagraph{Analytical chemistry}
\variable{output/question_count_per_dir/json_file_counts_analytical_chemistry.txt} questions are based on master student examination papers at the University of Jena (Germany). 
These questions focus on the principles and techniques employed in analytical chemistry.

\subparagraph{Combustion engineering}
\variable{output/question_count_per_dir/json_file_counts_combustion_engineering.txt} questions are based on master student examination papers at the University of Magdeburg (Germany). 
They explore topics related to combustion processes and engineering principles.

\subparagraph{Functional materials and nanomaterials}
\variable{output/question_count_per_dir/json_file_counts_func_mats_and_nanomats.txt}  questions are based on exercises in a seminar conducted at the University of Jena (Germany), delving into topics concerning functional materials and nanomaterials, exploring their properties and applications.

@@

\subparagraph{Textbook questions}
\variable{output/question_count_per_dir/json_file_counts_oup.txt} questions are based on questions from various textbooks covering biomolecular science, drug synthesis, molecular structure, organic chemistry, and X-ray crystallography.
